Horizontal aggregation of spatially biased ecosystem condition indicators – a GIS based workflow

### 2024-04-09 manuscript/Manuscript.qmd

# #define colours for dots and bars
dotCOLS = c("grey90","grey70", "grey50", "grey40")
barCOLS <- tmaptools::get_brewer_pal("Set1", n = 4)

(forest_plot <- stats_tbl |>
  mutate(
    indicator = case_when(
      indicator == "i_ADSV" ~ "ADSV",
      indicator == "i_alien" ~ "Alien species",
      indicator == "i_ditch" ~ "Trenching"
    )
  ) |>
  rowwise() |>
  mutate(
    low = quantile(rnorm(200, mean, sd), probs = 0.025),
    high = quantile(rnorm(200, mean, sd), probs = 0.975),
    high = ifelse(high > 1, 1, high)
  ) |>
  ggplot(aes(x=infrastructureIndex, 
             y=mean, 
             ymin=low,
             ymax=high,
             col=factor(infrastructureIndex),
             fill=factor(infrastructureIndex))) + 
  geom_linerange(
    size=10) +
  geom_point(
    size=3, 
    shape=21, 
    colour="white", 
    stroke = 0.5,
    ) +
  geom_text(
    aes(y = low, label = n),
    nudge_y = -0.1,
    show.legend = F
  ) +
  scale_fill_manual(values=dotCOLS)+
  scale_color_manual(values=barCOLS)+
  scale_x_discrete(name="") +
  scale_y_continuous(name="Indicator values", limits = c(-0.1, 1)) +
  coord_flip() +
  theme_bw() +
  labs(fill = "HIA",
       col = "HIA") +
  facet_grid(indicator ~ Municipality)
)

ggsave("../images/forest-plot.jpg",
       plot=forest_plot,
       width = 8,
       height = 6)
```

@@

# #define colours for dots and bars
dotCOLS = c("grey90","grey70", "grey50", "grey40")
barCOLS <- tmaptools::get_brewer_pal("Set1", n = 4)

(forest_plot_ex <- stats_tbl |>
  filter(indicator == "i_ditch",
         Municipality == "Nord-Aurdal") |>
  rowwise() |>
  mutate(
    low = quantile(rnorm(200, mean, sd), probs = 0.025),
    high = quantile(rnorm(200, mean, sd), probs = 0.975),
    high = ifelse(high > 1, 1, high)
  ) |>
  ggplot(aes(x=infrastructureIndex, 
             y=mean, 
             ymin=low,
             ymax=high,
             col=factor(infrastructureIndex),
             fill=factor(infrastructureIndex))) + 
  geom_linerange(
    size=10) +
  geom_point(
    size=3, 
    shape=21, 
    colour="white", 
    stroke = 0.5,
    ) +
  scale_fill_manual(values=dotCOLS)+
  scale_color_manual(values=barCOLS)+
  scale_x_discrete(name="") +
  scale_y_continuous(name="Indicator values", limits = c(.7, 1)) +
  coord_flip() +
  theme_bw() +
  labs(fill = "HIA",
       col = "HIA")
)

#ggsave(plot = forest_plot_ex,
#       "../images/forest-plot-ex.jpg",
#       width=3,
#       height = 3)
```

>>>>

# #define colours for dots and bars
dotCOLS = c("grey90","grey70", "grey50", "grey40")
#barCOLS <- tmaptools::get_brewer_pal("Set1", n = 4)
barCOLS <- c("#fff7bd", "#fecf66", "#f88b22", "#cc4c02")

(forest_plot <- stats_tbl |>
  mutate(
    indicator = case_when(
      indicator == "i_ADSV" ~ "ADSV",
      indicator == "i_alien" ~ "Alien species",
      indicator == "i_ditch" ~ "Trenching"
    )
  ) |>
  rowwise() |>
  mutate(
    low = quantile(rnorm(200, mean, sd), probs = 0.025),
    high = quantile(rnorm(200, mean, sd), probs = 0.975),
    high = ifelse(high > 1, 1, high)
  ) |>
  ggplot(aes(x=infrastructureIndex, 
             y=mean, 
             ymin=low,
             ymax=high
             )) + 
  geom_linerange(
    aes(colour=factor(infrastructureIndex)),
    size=10) +
  geom_point(
    aes(fill=factor(infrastructureIndex)),
    size=3, 
    shape=21, 
    colour="white", 
    stroke = 0.5,
    ) +
  geom_text(
    aes(y = low, label = n),
    nudge_y = -0.1,
    show.legend = F
  ) +
  scale_fill_manual(values=rev(dotCOLS))+
  scale_color_manual(values=barCOLS)+
  scale_x_discrete(name="") +
  scale_y_continuous(name="Indicator values", limits = c(-0.1, 1)) +
  coord_flip() +
  theme_bw() +
  labs(fill = "HIA",
       col = "HIA") +
  facet_grid(indicator ~ Municipality)
)

#ggsave("../images/forest-plot.jpg",
#       plot=forest_plot,
#       width = 8,
#       height = 6)
```

@@

(forest_plot_ex <- stats_tbl |>
  filter(indicator == "i_ditch",
         Municipality == "Nord-Aurdal") |>
  rowwise() |>
  mutate(
    low = quantile(rnorm(200, mean, sd), probs = 0.025),
    high = quantile(rnorm(200, mean, sd), probs = 0.975),
    high = ifelse(high > 1, 1, high)
  ) |>
  ggplot(aes(x=infrastructureIndex, 
             y=mean, 
             ymin=low,
             ymax=high,
             col=factor(infrastructureIndex),
             fill=factor(infrastructureIndex))) + 
  geom_linerange(
    size=10) +
  geom_linerange(
    size=10,
    lwd=1,
    colour="black") +
  geom_point(
    size=3, 
    shape=21, 
    colour="white", 
    stroke = 0.5,
    ) +
  scale_fill_manual(values=rev(dotCOLS))+
  scale_color_manual(values=barCOLS)+
  scale_x_discrete(name="") +
  scale_y_continuous(name="Indicator values", limits = c(.7, 1)) +
  coord_flip() +
  theme_bw() +
  labs(fill = "HIA",
       col = "HIA")
)

ggsave(plot = forest_plot_ex,
       "../images/forest-plot-ex.jpg",
       width=3,
       height = 3)
```
